---
title: "Ecological Behaviour Analysis in Malaysia"
author: "Yeo Xiu Juan"
date: "24 April 2022"
output:
  html_document: 
    prettydoc::html_pretty:
      theme: architect
    highlight: espresso
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
editor_options: 
  chunk_output_type: inline
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = T)


```

```{css, echo = F}

h1 { color: rgb(62, 6, 148); }62
h2 { color: rgb(0, 104, 139); } 
h3 { color: rgb(51, 122, 183); }

body {font-family: -apple-system, 
                   BlinkMacSystemFont, 
                   "Segoe UI", 
                   Roboto, 
                   Ubuntu;
      font-size: 12pt; }

code { color: rgb(205,79,57) }

.tocify-extend-page {height: 0 !important; }


```

## Problem Statement

Sustainability literacy is about demonstrating one's awareness of sustainability and its complex relationships in the environment and society. It is about possessing the necessary information, knowledge, skills and mindsets that allow individuals to commit, formulate and communicate sustainable solutions through multidisciplinary approaches.

Malaysia ranked 132nd in the Global Sustainability index.The country was also a global leader in plastic manufacturing.One of the key challenge the country faced was plastic pollution. Plastic waste contain toxic chemical that can seriously impair health.

Therefore, the purpose of this study will analyse Malaysian's literacy towards sustainability and which factor impair them from saving the planet.

## What will be investigated ?

1.  Do gender make a difference when come to environmental awareness?

2.  Do income drive away sustainability ?

```{r}
# Load necessary packages
pacman::p_load(haven,tidyverse, lubridate, 
               gtrendsR, rvest, glue, rtweet,
               gridExtra, scales, ggthemes, sandwich)

library(haven)
```

## Import SPSS DataSet (Original Data)

```{r}
green_malaysia <- read_sav("C:\\Users\\joyce\\OneDrive\\Desktop\\dasr2022\\green consumption data.sav")

glimpse(green_malaysia)
```

Remove unwanted Variable

```{r}

library(data.table)

clean_data <-green_malaysia     
  setDT(clean_data)[, c("ID",
                        "Marital_status","No_household","Occupation",
                        "Work_category",
                        "TotalEC",
                        "TotalSI",
                        "TotalPBC",
                        "TotalCNS",
                        "TotalGC")
                      := NULL]
glimpse(clean_data)
```

Tidy all the variables to Numeric / Factor

```{r}

# Environment Concern (EC) 

clean_data$EC1 <- as.numeric(clean_data$EC1)
clean_data$EC2 <- as.numeric(clean_data$EC2)
clean_data$EC3 <- as.numeric(clean_data$EC3)
clean_data$EC4 <- as.numeric(clean_data$EC4)
clean_data$EC5 <- as.numeric(clean_data$EC5)
clean_data$EC6 <- as.numeric(clean_data$EC6)

# Social Influence

clean_data$SI1 <- as.numeric(clean_data$SI1)
clean_data$SI2 <- as.numeric(clean_data$SI2)
clean_data$SI3 <- as.numeric(clean_data$SI3)
clean_data$SI4 <- as.numeric(clean_data$SI4)


# Perceive Behavioural Control (PBC) 
clean_data$PBC1 <- as.numeric(clean_data$PBC1)
clean_data$PBC2 <- as.numeric(clean_data$PBC2)
clean_data$PBC3 <- as.numeric(clean_data$PBC3)
clean_data$PBC4 <- as.numeric(clean_data$PBC4)
clean_data$PBC5 <- as.numeric(clean_data$PBC5)


# Green Consumption Behaviour (GC) 
clean_data$GC1 <- as.numeric(clean_data$GC1)
clean_data$GC2 <- as.numeric(clean_data$GC2)
clean_data$GC3 <- as.numeric(clean_data$GC3)
clean_data$GC4 <- as.numeric(clean_data$GC4)
clean_data$GC5 <- as.numeric(clean_data$GC5)
clean_data$GC6 <- as.numeric(clean_data$GC6)
clean_data$GC7 <- as.numeric(clean_data$GC7)
clean_data$GC8 <- as.numeric(clean_data$GC8)
clean_data$GC9 <- as.numeric(clean_data$GC9)
clean_data$GC10 <- as.numeric(clean_data$GC10)
clean_data$GC11 <- as.numeric(clean_data$GC11)
clean_data$GC12 <- as.numeric(clean_data$GC12)
clean_data$GC13 <- as.numeric(clean_data$GC13)


# Consumer Novelty Seeking

clean_data$CNS1 <- as.numeric(clean_data$CNS1)
clean_data$CNS2 <- as.numeric(clean_data$CNS2)
clean_data$CNS3 <- as.numeric(clean_data$CNS3)
clean_data$CNS4 <- as.numeric(clean_data$CNS4)
clean_data$CNS5 <- as.numeric(clean_data$CNS5)
clean_data$CNS6 <- as.numeric(clean_data$CNS6)
clean_data$CNS7 <- as.numeric(clean_data$CNS7)
clean_data$CNS8 <- as.numeric(clean_data$CNS8)

# Media Preference
clean_data$PM1 <- as.numeric(clean_data$PM1)
clean_data$PM2 <- as.numeric(clean_data$PM2)
clean_data$PM3 <- as.numeric(clean_data$PM3)
clean_data$PM4 <- as.numeric(clean_data$PM4)
clean_data$PM5 <- as.numeric(clean_data$PM5)


# Gender  # Female = 2 , Male 1 > Categorical Variable
clean_data$Gender <- as.factor(clean_data$Gender)

# Age > Categorical Variable
clean_data$Age <- as.factor(clean_data$Age)

# Education > Categorical Variable
clean_data$Education  <- as.factor(clean_data$Education)

# Income > Categorical Variable
clean_data$Income  <- as.factor(clean_data$Income)

# Ethnicity > Categorical Variable

clean_data$Ethnicity   <- as.factor(clean_data$Ethnicity)

glimpse(clean_data)

```


```{r}
# View if the variable is normally distribute 
install.packages("skimr")
library(skimr)
skim(clean_data)
```


Tidy & Transform "Clean Data" to "Green Data"

```{r}
green_data <- clean_data %>% 
  mutate(green_decision = rowMeans(clean_data %>% select(starts_with("PBC") 
                                                       )
                                  ),
  green_behaviour = rowMeans(clean_data %>% select(starts_with("GC") 
                                                  )
                            ),
  green_concern = rowMeans(clean_data %>% select(starts_with("EC") 
                                               )
                        ),
  
  green_Infulence = rowMeans(clean_data %>% select(starts_with("SI")  
                                                )
                          ),
  
  green_seeking = rowMeans(clean_data %>% select(starts_with("CNS")
                                                )
                                                 
                            )
         )
```

Rename gender from Original Data : 1 = Male , 2 = Female

```{r}
green_data <- green_data %>% 
  mutate(female = ifelse(Gender == 2, 1, 0) 
        ) %>% 
  select(-Gender)

green_data <- green_data[ , -(1:41)]

glimpse(green_data)
```

# Model

For the preparation of the model, correlational matrix was run and to analyse these variables (within the model) are related.

```{r}
pacman::p_load(Hmisc, broom, DT)

green_data %>% 
  as.matrix(.) %>% 
  Hmisc::rcorr(.) %>% 
  broom::tidy(.) %>% 
  rename(variable_1 = column1,
         variable_2 = column2,
          corr = estimate) %>% 
  mutate(abs_corr = abs(corr)
        ) %>% 
  datatable(options = list(scrollX = T),
                ) %>%
  formatRound(columns = c("corr", "p.value", "abs_corr"), 
              digits = 3)
```

```{r}
## Cutting-edge assumption check ----
library(gvlma)
library(car)

            
```

## OLS Models

4 models will be conducted to address malaysian's ecological awareness and attitude towards sustainability .

[**Model 1 & 2 : Green Decision X Income**]{.ul}

-   Model 1 Main Effect

\$\$ \begin{eqnarray}
\widehat{greenbehaviour} = intercept + b_1green_decision + b_2Age + b_3Education+ b_4Income + b_5Ethicity + b_6female +  \epsilon\\ 

\end{eqnarray} \$\$ Our key investigation lies in the next model, in which we regressed income and green decision orientations, along with interaction terms, onto Green Behaviour(`model2`).

-   Model 2 Interaction model

$$
\begin{eqnarray}
\widehat{greenbehaviour} = intercept + b_1green_decision + b_2Age + b_3Education+ b_4Income + b_5Ethicity + b_6female +  \\ 
                    + b_7female \times green decision + b_8age\times green decision + b_9education \times green decision + b_10Ethnicity \times green decision + \epsilon
\end{eqnarray}
$$

[**Mean Centering for Model 1 & 2**]{.ul}

```{r}
Centered_data_m1 <- green_data %>% 
  mutate_at(vars(-c(green_behaviour,female) 
            ), 
  ~(. - mean(., na.rm = T)))
      
```

```{r}
model1 <- Centered_data_m1 %>% 
  lm(formula = green_behaviour ~ green_decision + Education + Income + female + Age + Ethnicity,   
     data = .) 

tidy(model1) %>% as_tibble()
glance(model1)
```

```{r}
model2 <- Centered_data_m1 %>% 
  lm(formula = green_behaviour ~ green_decision *( Age + Education + female + Ethnicity + Income),
     data = .) 

tidy(model2) %>% as_tibble()
glance(model2)
```

The results of the analysis suggest that adding the interaction terms significantly increases the R-squared of \`model2\`, as compared to \`model1\`.

[**Assumption Check for Model 2**]{.ul}

```{r fig.align="center", fig.height=10, fig.width=10, warning=FALSE}
library(gvlma)
gvlma(model2)
```

```{r}
library(ggthemes)
theme_set(theme_fivethirtyeight())

library(ggfortify)
autoplot(gvlma(model2))
```

[**Check Multicollinearity for Model 1 & 2**]{.ul}

```{r fig.align = "center", fig.width = 10, fig.height= 10}
library(car)
vif(model1);vif(model2)

```

```{r set up ,echo=FALSE}
library(knitr)
library(kableExtra)
```

[**Model 2 Result using `kable` in `R Markdown`**]{.ul}

```{r}
kable(tidy(model2))%>%
  kable_paper("striped", full_width = T, fixed_thead = T) %>%
  column_spec(c(1, 5), bold = T) %>%
  row_spec(0, bold = T,color = "Black",background = "#D3D3D3") %>% 
  row_spec(c(2, 4, 6, 8, 10), color = "Black", background = "#E6E6FA")

kable(glance(model2))%>%
  kable_paper("striped", full_width = T, font_size = 12) %>%
  column_spec(c(2, 4, 6, 8, 10,12), bold = T, color = "white", background = "#ff6347")

```

The regression analysis result shows that appears that the relationships between income and green perceive affect the green behaviour.

## Visualize for (Model 2)

[***Green Decision x Income***]{.ul}

```{r}
library(modelr)

Centered_data_m1 %>% summarise(sd(Income ))

```

-   The data for gender was not equally distributed, therefore the most frequent gender female that denotes as ("1") was selected for the analysis.

```{r}
grid_group3_model2 <- Centered_data_m1 %>% 
  data_grid(green_decision, Income = c(-1.13, 0.00, 1.13),
            female = 1, Age = 0, Education = 0,Ethnicity = 0) %>% 
  add_predictions(model2) %>% 
  rename(predicted_green_behaviour = pred)

grid_group3_model2
```

[Undo the mean centering for (`green decision`) variable .]{.ul}

```{r}
grid <- grid_group3_model2 %>% 
  mutate(green_decision= green_decision + mean(green_data$green_decision), Income = factor(as.double(factor(Income))))

grid
```

GGplot on predicted_green_behaviour

```{r}
ggplot(grid, aes(x = green_decision , y = predicted_green_behaviour, color = factor(Income))) +
  geom_point(size=3) + 
  scale_color_discrete(breaks = c(1,2,3), label=c("Low", "Average","High")) +
  geom_segment(aes(x=green_decision, 
                   xend=green_decision, 
                   y=2.5, 
                   yend=predicted_green_behaviour)) + 
  coord_cartesian(ylim = c(2.5, 3.4),
                  xlim = c(2.4, 3.0)) +
  theme_bw() +                 
  labs(title="Green Decision X Income", 
       subtitle="Green Consumption perceive Behaviour ", 
       caption="source: mpg")


```

The above dot plot represent that the level of income green consumption behaviour.

As from the above dot plot, we could see the higher income level will have higher green consumption.

```{r}
pacman::p_load(jtools, huxtable, ggstance, interactions,grid.Extra,sandwich)
```

```{r fig.align = "center", fig.width = 10, fig.height= 12, warning = F}

export_summs(model1, model2, 
             error_format = "(t = {statistic}, p = {p.value})",
             align = "right",
             model.names = c("Main Effects Only", "with Interactions"),
             digits = 3)

```

```{r}
plot_summs(model1, model2, 
           scale = T,
           plot.distributions = T,
           model.names = c("Main Effects Only", "with Interactions")) +
  theme(legend.position = "top")
```

[**Undid the mean centering for Model 2**]{.ul}

```{r}
model2_WO_center <-  green_data %>% 
  lm(formula = green_behaviour ~ green_decision *( Age + Education + female + Ethnicity + Income),
     data = .)
```

Step 1: Plot interaction using interact_plot(interval = T) ----

```{r}
interact_plot(model = model2_WO_center, # plug-in your model
              pred = green_decision, # pred = predictor = X1 = Explanatory
              modx = Income, # modx = moderator = X2
              modx.labels = c("Low Income",
                              "Average Income",
                              "High Income"),
              legend.main = "Income",
              colors = c("sandybrown", 
                         "deepskyblue3",
                         "orangered1"),
              interval = T # display confidence intervals
              ) +
  theme(legend.position = "top")
```

Step 2 : Run simple slopes analysis

```{r}
sim_slopes(model2_WO_center,
           pred = green_decision, 
           modx = Income,
           johnson_neyman = F)
```

Step 3: Spotlight analysis

```{r}
sim_slopes(model2_WO_center,
           pred = Income, 
           modx = green_decision,
           johnson_neyman = T)
```

Step 4: Run interaction_plot() again by adding benchmark for regions of significance

```{r}
interact_plot(model = model2_WO_center, # plug-in your model
              pred = green_decision, # pred = predictor = X1 = Explanatory
              modx = Income, # modx = moderator = X2
              modx.labels = c("Low Income",
                              "Average Income",
                              "High Income"),
              legend.main = "Income",
              colors = c("sandybrown", 
                         "deepskyblue3",
                         "orangered1"),
              interval = T # display confidence intervals
              ) +
  theme(legend.position = "top") +
  geom_vline(xintercept = 4.73,
             color = "red",
             size = 1.5) + 
  annotate("rect",
           fill = "yellow",
           xmin = 4.73,
           xmax = 5.0,
           ymin = 2.4,
           ymax = 5.0,
           alpha = 0.10) + 
  annotate("text",
           x = 4.3,
           y = 4.3,
           label = "The shaded area denotes\nthe regions of significance\nbased on alpha at 5%")
```

Step 5: Finalize the figure by adding necessary information

```{r fig.align = "center", fig.width = 10, fig.height= 12, warning = F}
interact_plot(model = model2_WO_center, 
              pred = green_decision, 
              modx = Income,
              modx.labels = c("Low Income",
                              "Average Income",
                              "High Income"),
              legend.main = "Income",
              colors = c("sandybrown", 
                         "deepskyblue3",
                         "orangered1"),
              interval = T ,# display confidence intervals
              plot.points = T, # reveal your data points
              jitter = 0.1) +
  theme(legend.position = "top") +   
  labs(y = "Green Consumption",
       x = "Green Perceive",
       title = "The Green Perceive on Income Level and Green Perceive\non Green Consumption",
       subtitle = "Income Level does not drive away green consumption",
       caption = "Source:  ") +
  geom_vline(xintercept = 4.73,
             color = "black",
             size = 1.0) + 
  annotate("rect",
           fill = "yellow",
           xmin = 4.73,
           xmax = 5.0,
           ymin = 2.4,
           ymax = 5.0,
           alpha = 0.10) + 
  annotate("text",
           x = 5.0,
           y = 5.2,
           label = "The shaded area denotes\nthe regions of significance\nbased on alpha at 5%")
  theme_fivethirtyeight() + 
  theme(legend.position = "top",
        axis.title = element_text(),
        text = element_text(family = "Courier")
        )

```

## [Interpretation for Model 1 & 2]{.ul}

Based on the analysis, it shows that income level does not drive away the green consumption. The gap between low and high income was not too far away . Even through from the reality, many could see that higher social consumer group may have greater perception of green behaviour.

Certainty, the ability to purchase green products are on the higher price than non-green products, but minimal effort such as making use of the daily resources could protect the the environment.

Green perceive behaviour and green consumption behaviour is based on observational study,leading to correlation causation in limitations and future directions.

## Visualize for (Model 4)

[**Model 3 & 4 : Green Seeking X Gender**]{.ul}

```{r}
Centered_data_m2 <- green_data %>% 
    mutate_at(vars(-c(green_behaviour,female)
    ), 
    ~(. - mean(., na.rm = T)
    )
    )
```

\$\$ \begin{eqnarray}
\widehat{greenbehaviour } = intercept + b_1greenseeking  + b_2Age + b_3Education+ b_4Income + b_5Ethicity + b_6Education + b_7female + b_8 green concern + \epsilon
\end{eqnarray}

$$
$$

\begin{eqnarray}
\widehat{greenbehaviour } = intercept + b_1greenseeking  + b_2Age + b_3Education+ b_4Income + b_5Ethicity + b_6Education + b_7female + b_8 green concern + \\
+b_9 Ethnicity \times green seeking + b_10 Income \times green seeking + b_11 Education \times green seeking + b_12 Age \times green seeking + b_13 female \times green seeking + +b_14 green concern + \epsilon

\end{eqnarray} \$\$

```{r}
model3 <- Centered_data_m2 %>% 
    lm(formula = 	green_behaviour ~ green_seeking + Age + Ethnicity + Income + Education + female + green_concern,
       data = .)
```

```{r}
model4 <- Centered_data_m2 %>% 
    lm(formula = green_behaviour ~ green_seeking *(Ethnicity + Income + Education  + Age + female)+ green_concern,
       data = .) 
```

```{r}
gvlma(model4)
```

```{r fig.align = "center", fig.width = 10, fig.height= 10, warning = F}

library(ggthemes)
theme_set(theme_fivethirtyeight())


library(ggfortify)
autoplot(gvlma(model4))
```

[**Check Multicollinearity for Model 3 & 4**]{.ul}

```{r}
vif(model3);vif(model4)
```

```{r}
kable(tidy(model4))%>%
  kable_paper("striped", full_width = T, fixed_thead = T) %>%
  column_spec(c(1, 5), bold = T) %>%
  row_spec(0, bold = T,color = "Black",background = "#D3D3D3") %>% 
  row_spec(c(2, 4, 6, 8, 10), color = "Black", background = "#E6E6FA")

kable(glance(model4))%>%
  kable_paper("striped", full_width = T, font_size = 12) %>%
  column_spec(c(2, 4, 6, 8, 10,12), bold = T, color = "white", background = "#ff6347")
```

```{r}
plot_summs(model3, model4,
           scale = T,
           plot.distributions = T,
           model.names = c("Main Effects Only", "with Interactions")) +
  theme(legend.position = "top")
```

```{r}
export_summs(model3,
             model4,
             model.names = c ("Main Effeects only",
                              "with Interaction"),
             error_format = "CIs = [{conf.low} , {conf.high}]",
             dights = 3
             )
```

The results of the analysis suggest that adding the interaction terms significantly increases the R-squared of \`model4\`, as compared to \`model3\`.

[Undo the mean centering for(green_seeking)variable .]{.ul}

```{r}
predicted_Y_value <- Centered_data_m2 %>% 
  modelr::data_grid(green_seeking, 
                    female, 
                    Age = 0 ,
                    Education  = 0,
                    Income = 0,
                    Ethnicity = 0 ,
                    green_concern = 0,
                    ) %>% 
  add_predictions(model4) %>% 
  rename(predicted_green_behaviour = pred)
```

```{r}
predicted_Y_value %>% 
  print(n = nrow(.)
        )
```

```{r}
predicted_Y_value <- predicted_Y_value %>% 
  mutate(green_seeking = green_seeking + mean(green_data$green_seeking)
         )
```

```{r}
predicted_Y_value %>% 
  print(n = nrow(.)
        )
```

```{r}
estimated <- predicted_Y_value %>% 
  ggplot(aes(x = green_seeking,
             y = predicted_green_behaviour,
             color = factor(female)
             )
         ) + 
  geom_line(size = 2) +
  scale_color_discrete(breaks = c(0, 1),
                       label = c("Male",
                                 "Female")
                       ) + 
  coord_cartesian(ylim = c(2.4, 3.0),
                  xlim = c(1.1, 1.6)
                  ) + 
  theme_bw() + 
  theme(legend.position = "top")

estimated 
```

From the above analysis, it shows that female seeks more green products than male.

```{r}
estimated_vs_observed <- ggplot(data = green_data, 
                                aes(x = green_seeking,
                                    y = green_behaviour)
                                ) + 
  geom_point(aes(color =factor(female)
                ),
             alpha = 0.25) + 
    geom_line(data = predicted_Y_value, 
              aes(y = predicted_green_behaviour,
                  color = factor(female)
                  ),
              size = 1.5
              ) +
  facet_wrap(. ~ factor(female),
             labeller = as_labeller(c("0" = "MALE",
                                      "1" = "FEMALE")
                                    )
              ) +
  coord_cartesian(ylim = c (2.4, 3.0),
                  xlim = c (1.1, 1.6)
                  ) +
  theme_bw() +
  theme(legend.position = "none")
```

```{r}
grid.arrange(estimated, estimated_vs_observed, ncol = 2)
```

```{r}
model4_WO_center <- green_data %>% 
    lm(formula = green_behaviour ~ green_seeking *(Ethnicity + Income + Education  + Age + female)+ green_concern,
       data = .) 
```

```{r}
install.packages("intearctions")
library(interactions)
```

[**Steps for Interpreting Model 4**]{.ul}

Step 1: Plot interaction using interact_plot(interval = T)

```{r}
interact_plot(model = model4_WO_center, 
              pred = green_seeking,
              modx = female, 
              modx.labels = c("0" = "Male",
                              "1" = "Female"),
              legend.main = "Gender",
              colors = c("tomato3",
                         "deepskyblue3"),
              interval = T 
              ) +
  theme(legend.position = "top")
```

Step 2: Run simple slopes analysis

```{r}
sim_slopes(model = model4_WO_center,
           pred = green_seeking,
           modx = female,
           johnson_neyman = F)
```

Step 3: Spotlight analysis

```{r}
sim_slopes(model = model4_WO_center,
           pred = female,
           modx = green_seeking,
           johnson_neyman = T)
```

Step 4: Run interaction_plot() again by adding benchmark for regions of significance

```{r fig.align = "center", fig.width = 10, fig.height= 10, warning = F}
interact_plot(model = model4_WO_center, 
              pred = green_seeking,
              modx = female,
              modx.labels = c("0" = "Male",
                              "1" = "Female"),
              legend.main = "Gender",
              colors = c("tomato3",
                         "deepskyblue3"),
              interval = T 
              ) +
  theme(legend.position = "top") + 
   geom_vline(xintercept = 6.57,
             color = "red",
             size = 1.5) + 
  annotate("rect",
           fill = "yellow",
           xmin = 6.57,
           xmax = 5.00,
           ymin = 1,
           ymax = 5,
           alpha = 0.10) + 
  annotate("text",
           x = 4.3,
           y = 4.3,
           label = "The shaded area denotes\nthe regions of significance\nbased on alpha at 5%")
```

Step 5: Finalize the figure by adding necessary information

```{r fig.align = "center", fig.width = 10, fig.height= 10, warning = F}
  
```

## [Interpretation for Model 3 & 4]{.ul}

Many studies have shown that many have the misconception of greenness is femininity.Men are often less eco-friednly than women due to fear of being teased by their sexual preference.From the analysis, we could see that when it comes to green consumption, Male and Female had the almost the same perception of green seeking as they are moving towards the upward trend.But we could also see that the predicted green seeking is out of the interval which shows that the gender norms and personality difference should not distract us from saving our planet everyday. The relationships between green consumption and green seeking is based on observational study,leading to correlations, not causations.

## Limitations and Future Directions

The data size was only from 375 respondent which is difficult to find the significant relationships. The purpose of this project was to provide a exploration on bridging the eco gender gap and the social class groups seeking for green environment.

## References

1.  <https://www.thestar.com.my/opinion/letters/2021/03/16/tackling-increasing-plastics-pollution-in-malaysia>
2.  <https://link.springer.com/article/10.1007/s42452-021-04234-y>
3.  <https://www.greeneconomycoalition.org/news-and-resources/should-green-consumption-mean-less-consumption>
4.  <https://www.ivint.org/what-is-the-eco-gender-gap-and-how-can-we-bridge-it/>

## run `sessionInfo()`

```{r}
sessionInfo()
```

## Contribution Statement

From searching for the right resources to the final project, I had applied what have been taught in the entire modules in R.

Even through there was up and down when pulling this project I have overcomed it and many thanks to Prof Roh and Zhen Wei.

Thank You
